Assignment: Referee Report

### 2024-08-29 assignments/research_proposal/response_to_reviewers.Rmd

---
title: |
        | Assignment: Response to Reviewers
subtitle: |
        | Ph.D. Environmental and Development Economics
        | UMN Applied Economics 2024
        | Instructor: Raahil Madhok
# Output type and options (no TOC and yes fig captions)
output:
  bookdown::pdf_document2: 
    toc: false
    fig_caption: yes
    # This also keeps the .tex file that is used to make the output (we will eventually need this for publication)
    keep_tex: yes

# This includes latex arguments
header-includes:
  - \input{header.tex}

---

**Due Date: October 10th, 2024**

# Overview
In this assignment, you will write a mock ``response to the reviewer'' based on the peer review you received for your research proposal. This process mimics the response letter you would write in a journal submission, where you address each comment made by the referee, explain how you revised the paper, and justify any decisions you made in response to the feedback.

The purpose of this exercise is to help you practice responding to critical feedback in a constructive and professional manner, while also improving your proposal based on your peer's suggestions.

# Structure of the Response

Your response should include the following components:

## Introduction Paragraph

- **Thank the reviewer**: Begin by thanking your reviewer for their thoughtful feedback
- **General summary**: Summarize the key points of the review and provide a brief overview of the changes you have made to your proposal as a result of the feedback.
- **Tone**: Keep your tone respectful, professional, and appreciative.

## Point-by-Point Response
For each comment made by the reviewer, provide a clear and detailed response. The unwritten rule is to copy and paste the peer review into a document, turn each comment into a bulletted list, and then respond underneath each comment in the list.

For each point:

- **Restate the reviewer’s comment**: Begin by restating the comment or suggestion. This ensures clarity and demonstrates that you fully understand the critique.

- **Explain your response**:
    - **If you have made changes**: Explain what specific changes you made to the proposal in response to the reviewer’s comment. Clearly identify where in the revised proposal these changes can be found (e.g., “We have revised Section 2, paragraphs 3 and 4, to clarify the theoretical framework and the role of environmental externalities.”).
    - **If you disagree with the comment**: Provide a reasoned explanation for why you have chosen not to make the suggested change. Be polite and respectful, offering evidence or justification for maintaining your original approach. For example, “While we appreciate this suggestion, we believe that keeping the focus on District-level data is more consistent with the existing literature.”

- **Detail the improvement**: Explain how the changes you made improve the overall quality and clarity of your proposal. This will help the reviewer see the value of the revisions.

## Conclusion Paragraph

- **Reaffirm gratitude**: Reiterate your appreciation for the reviewer’s input.
- **Summary of revisions**: Offer a final summary of the revisions made and express your confidence that the proposal has been strengthened as a result.

# Guidelines for Writing Your Response

- **Be thorough**: Ensure that every comment in the review, whether major or minor, receives a response. Do not skip any points.

- **Be specific**: When describing the changes you made, be as specific as possible. Reference the exact sections or pages of your proposal where you incorporated changes.

- **Be polite and constructive**: Even if you disagree with some of the reviewer’s suggestions, maintain a respectful tone. Use evidence and logical reasoning to support your decisions.

- **Reflect improvements**: Make sure the changes you discuss in your response are actually incorporated into the revised version of your proposal. Your response and your revised proposal should be fully aligned.

# Format

- **Length:** Responses (not including the original comment) should not exceed 4 pages (1000 words)

- **Format:** 12 point font, double spaced, 1 inch margins

- **Submission:** PDF document (latex or word)

# Rubric
\begin{table}[h!]
\centering
\begin{tabular}{|l|p{8cm}|c|c|}
\hline
\textbf{Category} & \textbf{Criteria} & \textbf{Points} & \textbf{Score} \\
\hline
\multirow{2}{*}{\textbf{Comprehensive Response}} & Addresses all major and minor points raised by the reviewer, with no comments left unaddressed. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Clarity and Specificity}} & Clearly provides a detailed, specific response to each comment. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Incorporation of Changes}} & Demonstrates thoughtful incorporation of reviewer suggestions into the proposal, with clear references to specific changes made. & 30 & \\
\hline
\multirow{2}{*}{\textbf{Justification for Disagreements}} & Provides clear and well-reasoned explanations for why certain suggestions were not incorporated, using evidence and logical reasoning. & 30 & \\
\hline
\multirow{2}{*}{\textbf{Tone and Professionalism}} & Maintains a respectful, professional, and constructive tone throughout the response, even when disagreeing. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Writing Quality}} & The response document is well-organized, with clear writing, correct grammar, and appropriate length. & 10 & \\
\hline
\multicolumn{3}{|r|}{\textbf{Total Points Possible:}} & \textbf{100} \\
\hline
\end{tabular}
\end{table}

### 2024-08-29 assignments/research_proposal/response_to_reviewers.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\input{header.tex}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Assignment: Response to Reviewers}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Ph.D.~Environmental and Development Economics\\
UMN Applied Economics 2024\\
Instructor: Raahil Madhok}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\textbf{Due Date: October 10th, 2024}

\hypertarget{overview}{%
\section{Overview}\label{overview}}

In this assignment, you will write a mock ``response to the reviewer'\,' based on the peer review you received for your research proposal. This process mimics the response letter you would write in a journal submission, where you address each comment made by the referee, explain how you revised the paper, and justify any decisions you made in response to the feedback.

The purpose of this exercise is to help you practice responding to critical feedback in a constructive and professional manner, while also improving your proposal based on your peer's suggestions.

\hypertarget{structure-of-the-response}{%
\section{Structure of the Response}\label{structure-of-the-response}}

Your response should include the following components:

\hypertarget{introduction-paragraph}{%
\subsection{Introduction Paragraph}\label{introduction-paragraph}}

\begin{itemize}
\tightlist
\item
  \textbf{Thank the reviewer}: Begin by thanking your reviewer for their thoughtful feedback
\item
  \textbf{General summary}: Summarize the key points of the review and provide a brief overview of the changes you have made to your proposal as a result of the feedback.
\item
  \textbf{Tone}: Keep your tone respectful, professional, and appreciative.
\end{itemize}

\hypertarget{point-by-point-response}{%
\subsection{Point-by-Point Response}\label{point-by-point-response}}

For each comment made by the reviewer, provide a clear and detailed response. The unwritten rule is to copy and paste the peer review into a document, turn each comment into a bulletted list, and then respond underneath each comment in the list.

For each point:

\begin{itemize}
\item
  \textbf{Restate the reviewer's comment}: Begin by restating the comment or suggestion. This ensures clarity and demonstrates that you fully understand the critique.
\item
  \textbf{Explain your response}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{If you have made changes}: Explain what specific changes you made to the proposal in response to the reviewer's comment. Clearly identify where in the revised proposal these changes can be found (e.g., ``We have revised Section 2, paragraphs 3 and 4, to clarify the theoretical framework and the role of environmental externalities.'').
  \item
    \textbf{If you disagree with the comment}: Provide a reasoned explanation for why you have chosen not to make the suggested change. Be polite and respectful, offering evidence or justification for maintaining your original approach. For example, ``While we appreciate this suggestion, we believe that keeping the focus on District-level data is more consistent with the existing literature.''
  \end{itemize}
\item
  \textbf{Detail the improvement}: Explain how the changes you made improve the overall quality and clarity of your proposal. This will help the reviewer see the value of the revisions.
\end{itemize}

\hypertarget{conclusion-paragraph}{%
\subsection{Conclusion Paragraph}\label{conclusion-paragraph}}

\begin{itemize}
\tightlist
\item
  \textbf{Reaffirm gratitude}: Reiterate your appreciation for the reviewer's input.
\item
  \textbf{Summary of revisions}: Offer a final summary of the revisions made and express your confidence that the proposal has been strengthened as a result.
\end{itemize}

\hypertarget{guidelines-for-writing-your-response}{%
\section{Guidelines for Writing Your Response}\label{guidelines-for-writing-your-response}}

\begin{itemize}
\item
  \textbf{Be thorough}: Ensure that every comment in the review, whether major or minor, receives a response. Do not skip any points.
\item
  \textbf{Be specific}: When describing the changes you made, be as specific as possible. Reference the exact sections or pages of your proposal where you incorporated changes.
\item
  \textbf{Be polite and constructive}: Even if you disagree with some of the reviewer's suggestions, maintain a respectful tone. Use evidence and logical reasoning to support your decisions.
\item
  \textbf{Reflect improvements}: Make sure the changes you discuss in your response are actually incorporated into the revised version of your proposal. Your response and your revised proposal should be fully aligned.
\end{itemize}

\hypertarget{format}{%
\section{Format}\label{format}}

\begin{itemize}
\item
  \textbf{Length:} Responses (not including the original comment) should not exceed 4 pages (1000 words)
\item
  \textbf{Format:} 12 point font, double spaced, 1 inch margins
\item
  \textbf{Submission:} PDF document (latex or word)
\end{itemize}

\hypertarget{rubric}{%
\section{Rubric}\label{rubric}}

\begin{table}[h!]
\centering
\begin{tabular}{|l|p{8cm}|c|c|}
\hline
\textbf{Category} & \textbf{Criteria} & \textbf{Points} & \textbf{Score} \\
\hline
\multirow{2}{*}{\textbf{Comprehensive Response}} & Addresses all major and minor points raised by the reviewer, with no comments left unaddressed. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Clarity and Specificity}} & Clearly provides a detailed, specific response to each comment. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Incorporation of Changes}} & Demonstrates thoughtful incorporation of reviewer suggestions into the proposal, with clear references to specific changes made. & 30 & \\
\hline
\multirow{2}{*}{\textbf{Justification for Disagreements}} & Provides clear and well-reasoned explanations for why certain suggestions were not incorporated, using evidence and logical reasoning. & 30 & \\
\hline
\multirow{2}{*}{\textbf{Tone and Professionalism}} & Maintains a respectful, professional, and constructive tone throughout the response, even when disagreeing. & 10 & \\
\hline
\multirow{2}{*}{\textbf{Writing Quality}} & The response document is well-organized, with clear writing, correct grammar, and appropriate length. & 10 & \\
\hline
\multicolumn{3}{|r|}{\textbf{Total Points Possible:}} & \textbf{100} \\
\hline
\end{tabular}
\end{table}

\end{document}

### 2024-08-29 assignments/paper_presentations/presentation_tips.tex
add lectures 1-5

---
title: |
        | Assignment: Paper Presentations
subtitle: |
        | Ph.D. Environment and Development Economics
        | UMN Department of Applied Economics
        | Instructor: Raahil Madhok
date: "`r Sys.Date()`"
# Output type and options (no TOC and yes fig captions)
output:
  bookdown::pdf_document2: 
    toc: false
    fig_caption: yes
    # This also keeps the .tex file that is used to make the output (we will eventually need this for publication)
    keep_tex: yes

# This includes latex arguments
header-includes:
  - \input{header.tex}

---

# Overview
The goal of this assignment is to prepare you for presenting at economics conferences. As you proceed through your PhD, and then into your careers, you will inevitably attend and present at such conferences. This first few times can be nerve-wracking.

@@

# Structure
One randomly-selected student will present a pre-assigned paper at the beginning of each lecture. All students will read **the same** paper, which can be found below and in the syllabus (highlighted in red). The selection procedure is as follows:

1. **Slides:** Before each lecture, you will each read the assigned paper and prepare **10 slides** summarizing the paper. These slides will be uploaded to Canvas. All students are required to submit summary slides each week regardless of whether you are chosen to present.

2. **The hat:** At the beginning of each lecture, I will put all your names in a hat

3. **Randomization:** I will select a student to present randomly **with replacement**. This means that your name goes back into the hat each week. Thus, you may present in more than once, **or not at all**.

4. **Presentation:** You will give a 10 minute "conference-style" presentation of the paper, with 5 minutes for Q&A. Presentation tips can be found below.

5. **Grades:** If you are never chosen to present, your grade will be based upon your slide submissions.

# Presentation Tips
Many of these tips were provided by \href{https://pages.uoregon.edu/cameron/vita/}{Trudy Cameron} to help students prepare for AERE sessions. \href{https://www.raahilmadhok.com/pdf/fra_slides.pdf}{Here} is an example of a recent presentation I gave (15 mins/15 slides) that follows these tips.

- Each presentation should have 10 slides (fewer is okay, but not more)
- Allocate about 1 minute per slide
- It helps to rehearse a couple of times to ensure it fits into the allotted time. It is considered poor form at conferences if you exceed your time.
- Do not present every detail. Your job is to summarize and entice people to read the full paper.
- Start your presentation with a single slide that succinctly bullets your: research question, setting, data, empirical strategy, and two key results. This previews the whole paper, and rest of the presentation is dedicating to elaborating each bullet. 
- Type and use one-line bullet points. Eye-tracking to a new line can interfere with quickly grasping a point. Don't leave just a single word on a wrapped line of a bullet point). Remove superfluous words.
- Since you only have 10 minutes, don't spend too much time on the literature review. Instead, state how your paper improves on the literature (i.e. contributions), but still include citations.
- Aim to show only one equation. Try to to talk ``about'' your equation rather than provide a detailed explanation of every term. You want to bring along the median audience member, not just dazzle the most sophisticated theorist/econometrician in the room.
- Try to not read your slides directly. The audience can read. The bullet points should guide what you say, which means rehearsal is important. Think carefully about how you will transition between slides.

# Rubric

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\input{header.tex}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Assignment: Paper Presentations}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Ph.D.~Environment and Development Economics\\
UMN Department of Applied Economics}
\author{}
\date{\vspace{-2.5em}2024-08-25}

\begin{document}
\maketitle

\hypertarget{overview}{%
\section{Overview}\label{overview}}

The goal of this assignment is to prepare you for presenting at economics conferences. As you proceed through your PhD, and then into your careers, you will inevitably attend and present at such conferences. This first few times can be nerve-wracking.

@@

\hypertarget{structure}{%
\section{Structure}\label{structure}}

One randomly-selected student will present a pre-assigned paper at the beginning of each lecture. All students will read \textbf{the same} paper, which can be found below and in the syllabus (highlighted in red). The selection procedure is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Slides:} Before each lecture, you will each read the assigned paper and prepare \textbf{10 slides} summarizing the paper. These slides will be uploaded to Canvas. All students are required to submit summary slides each week regardless of whether you are chosen to present.
\item
  \textbf{The hat:} At the beginning of each lecture, I will put all your names in a hat
\item
  \textbf{Randomization:} I will select a student to present randomly \textbf{with replacement}. This means that your name goes back into the hat each week. Thus, you may present in more than once, \textbf{or not at all}.
\item
  \textbf{Presentation:} You will give a 10 minute ``conference-style'' presentation of the paper, with 5 minutes for Q\&A. Presentation tips can be found below.
\item
  \textbf{Grades:} If you are never chosen to present, your grade will be based upon your slide submissions.
\end{enumerate}

\hypertarget{presentation-tips}{%
\section{Presentation Tips}\label{presentation-tips}}

Many of these tips were provided by \href{https://pages.uoregon.edu/cameron/vita/}{Trudy Cameron} to help students prepare for AERE sessions. \href{https://www.raahilmadhok.com/pdf/fra_slides.pdf}{Here} is an example of a recent presentation I gave (15 mins/15 slides) that follows these tips.

\begin{itemize}
\tightlist
\item
  Each presentation should have 10 slides (fewer is okay, but not more)
\item
  Allocate about 1 minute per slide
\item
  It helps to rehearse a couple of times to ensure it fits into the allotted time. It is considered poor form at conferences if you exceed your time.
\item
  Do not present every detail. Your job is to summarize and entice people to read the full paper.
\item
  Start your presentation with a single slide that succinctly bullets your: research question, setting, data, empirical strategy, and two key results. This previews the whole paper, and rest of the presentation is dedicating to elaborating each bullet.
\item
  Type and use one-line bullet points. Eye-tracking to a new line can interfere with quickly grasping a point. Don't leave just a single word on a wrapped line of a bullet point). Remove superfluous words.
\item
  Since you only have 10 minutes, don't spend too much time on the literature review. Instead, state how your paper improves on the literature (i.e.~contributions), but still include citations.
\item
  Aim to show only one equation. Try to to talk ``about'\,' your equation rather than provide a detailed explanation of every term. You want to bring along the median audience member, not just dazzle the most sophisticated theorist/econometrician in the room.
\item
  Try to not read your slides directly. The audience can read. The bullet points should guide what you say, which means rehearsal is important. Think carefully about how you will transition between slides.
\end{itemize}

\hypertarget{rubric}{%
\section{Rubric}\label{rubric}}

@@

\end{document}

### 2024-08-29 assignments/research_proposal/peer_review.tex
add lectures 1-5

---
title: |
        | Assignment: Referee Report
subtitle: |
        | Ph.D. Environmental and Development Economics
        | UMN Applied Economics 2024
        | Instructor: Raahil Madhok
# Output type and options (no TOC and yes fig captions)
output:
  bookdown::pdf_document2: 
    toc: false
    fig_caption: yes
    # This also keeps the .tex file that is used to make the output (we will eventually need this for publication)
    keep_tex: yes

# This includes latex arguments
header-includes:
  - \input{header.tex}

---

**Due Date: October 10th, 2024**

# Overview
In this assignment, you will conduct a peer review of a classmate's research proposal. Peer reviewing is a critical skill in the academic community, where you assess the quality, clarity, and originality of others' work while providing constructive feedback.

On the evening that you submit your first draft (Oct. 3rd), you will receive a classmate's proposal to review. This will be a double-blind process so that neither of you will know who's proposal you are reviewing.

@@

# Structure of the Peer Review

## Major Points (Minimum 5 items)
The major points should highlight the most critical issues in the proposal. Below are some questions to think about as your identify your major points. You do not necessarily need to come up with criticism under each heading. You may, for example, identify two major criticisms in the theory and none in the research design.

- **The Research Question:** Is the question clear, well-motivated, and significant within the field of environmental and development economics? Does it have a clear connection to both theory and real-world policy relevance?

- **Theoretical Framework:** Is the theoretical framework well-developed and logically consistent? Does it directly relate to the research questions in a meaningful way? Are the assumptions justified? If the author is adapting an existing model, does the adaptation generate new and meaningful insights?

- **Research Design:** Is the empirical strategy clearly stated? Does the design convincingly address the research question? Are all of the identification assumptions addressed? Is there a different research design that may have yielded better identification?

- **Data Sources:** Does the proposal rely on real, available data, and is the data appropriate for the research question? Are there any concerns about data access, quality, or relevance that could hinder the feasibility of the research?

- **Policy Implications:** Does the proposal clearly discuss how the results of the research could influence policy decisions? Are the potential implications grounded in the real-world context?

## Minor Points (Minumum 5 items)
The minor points are smaller issues that, while less critical than the major points, can still enhance the quality and clarity of the proposal. These might include:

- Clarity of the writing (grammar, organization, and structure),
- Minor inconsistencies in the theoretical argument,
- Specific technical clarifications needed in the research design or data analysis,
- Suggestions for additional literature that could strengthen the theoretical framework,
- Formatting issues or citation inaccuracies.
- For each minor point, include:

# Writing Style
When writing your peer review, keep in mind the following guidelines:

- Be constructive. Frame your comments in a way that helps the author improve. For example, instead of saying "The research question is unclear," say, "The research question could be clarified by focusing more on the causal relationship between X and Y."

- Be specific. Provide clear examples and references to specific sections of the proposal. Vague comments like "Improve the theoretical framework" are less helpful than "On page 3, the author should elaborate on how the proposed model incorporates environmental externalities."

- Be respectful. Even if you find serious flaws in the proposal, present your feedback respectfully and professionally. Academic critique should be rigorous but fair.

- Balance criticism with praise. Highlight what the author has done well. This not only encourages them but also makes your review more balanced.

# Format

- **Style:** Each point (major or minor) should be clearly numbered or bulletted.

- **Length:** 4 pages max (1000 words)

- **Format:** 12 point font, double spaced, 1 inch margins

- **Submission:** PDF document (latex or word)

\newpage
# Rubric

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\input{header.tex}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Assignment: Referee Report}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Ph.D.~Environmental and Development Economics\\
UMN Applied Economics 2024\\
Instructor: Raahil Madhok}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\textbf{Due Date: October 10th, 2024}

\hypertarget{overview}{%
\section{Overview}\label{overview}}

In this assignment, you will conduct a peer review of a classmate's research proposal. Peer reviewing is a critical skill in the academic community, where you assess the quality, clarity, and originality of others' work while providing constructive feedback.

On the evening that you submit your first draft (Oct.~3rd), you will receive a classmate's proposal to review. This will be a double-blind process so that neither of you will know who's proposal you are reviewing.

@@

\hypertarget{structure-of-the-peer-review}{%
\section{Structure of the Peer Review}\label{structure-of-the-peer-review}}

\hypertarget{major-points-minimum-5-items}{%
\subsection{Major Points (Minimum 5 items)}\label{major-points-minimum-5-items}}

The major points should highlight the most critical issues in the proposal. Below are some questions to think about as your identify your major points. You do not necessarily need to come up with criticism under each heading. You may, for example, identify two major criticisms in the theory and none in the research design.

\begin{itemize}
\item
  \textbf{The Research Question:} Is the question clear, well-motivated, and significant within the field of environmental and development economics? Does it have a clear connection to both theory and real-world policy relevance?
\item
  \textbf{Theoretical Framework:} Is the theoretical framework well-developed and logically consistent? Does it directly relate to the research questions in a meaningful way? Are the assumptions justified? If the author is adapting an existing model, does the adaptation generate new and meaningful insights?
\item
  \textbf{Research Design:} Is the empirical strategy clearly stated? Does the design convincingly address the research question? Are all of the identification assumptions addressed? Is there a different research design that may have yielded better identification?
\item
  \textbf{Data Sources:} Does the proposal rely on real, available data, and is the data appropriate for the research question? Are there any concerns about data access, quality, or relevance that could hinder the feasibility of the research?
\item
  \textbf{Policy Implications:} Does the proposal clearly discuss how the results of the research could influence policy decisions? Are the potential implications grounded in the real-world context?
\end{itemize}

\hypertarget{minor-points-minumum-5-items}{%
\subsection{Minor Points (Minumum 5 items)}\label{minor-points-minumum-5-items}}

The minor points are smaller issues that, while less critical than the major points, can still enhance the quality and clarity of the proposal. These might include:

\begin{itemize}
\tightlist
\item
  Clarity of the writing (grammar, organization, and structure),
\item
  Minor inconsistencies in the theoretical argument,
\item
  Specific technical clarifications needed in the research design or data analysis,
\item
  Suggestions for additional literature that could strengthen the theoretical framework,
\item
  Formatting issues or citation inaccuracies.
\item
  For each minor point, include:
\end{itemize}

\hypertarget{writing-style}{%
\section{Writing Style}\label{writing-style}}

When writing your peer review, keep in mind the following guidelines:

\begin{itemize}
\item
  Be constructive. Frame your comments in a way that helps the author improve. For example, instead of saying ``The research question is unclear,'' say, ``The research question could be clarified by focusing more on the causal relationship between X and Y.''
\item
  Be specific. Provide clear examples and references to specific sections of the proposal. Vague comments like ``Improve the theoretical framework'' are less helpful than ``On page 3, the author should elaborate on how the proposed model incorporates environmental externalities.''
\item
  Be respectful. Even if you find serious flaws in the proposal, present your feedback respectfully and professionally. Academic critique should be rigorous but fair.
\item
  Balance criticism with praise. Highlight what the author has done well. This not only encourages them but also makes your review more balanced.
\end{itemize}

\hypertarget{format}{%
\section{Format}\label{format}}

\begin{itemize}
\item
  \textbf{Style:} Each point (major or minor) should be clearly numbered or bulletted.
\item
  \textbf{Length:} 4 pages max (1000 words)
\item
  \textbf{Format:} 12 point font, double spaced, 1 inch margins
\item
  \textbf{Submission:} PDF document (latex or word)
\end{itemize}

\newpage

\hypertarget{rubric}{%
\section{Rubric}\label{rubric}}
